\documentclass{article}

\title{Sorting Algorithms Study}
\author{Mir Ashikur Rahman (2003109), Barik (2003071), \\
        Md. Atik Mouhtasim (2003118), Partha Paul (2003078), \\
        Md. Abu Sufyan (2003085), Tameem Rahman (2003089)}

\begin{document}

\maketitle

\section*{Contributions}

\subsection*{Mir Ashikur Rahman (2003109)}
Wrote code to check runtime with different input sizes. Used Matplotlib to plot the collected data. Added figures and tables to the results and analysis section. Included a conclusion about the results study and data analysis.

\subsection*{Md Barkullah (2003071)}
Collected data on insertion and selection sort. Wrote Abstract, Introduction, and Background study. Explained how selection sort and insertion sort work with step-by-step figures.

\subsection*{Md. Atik Mouhtasim (2003118)}
Wrote the entire LaTeX code of the article, excluding the references part. Worked on figures and gave recommendations to the slide team. Created this document file.

\subsection*{Partha Paul (2003078)}
Created the BibTeX, added citations, wrote the algorithms, and helped Atik (2003118) make decisions. Adjusted the paper writing part, including writing the loop invariant, regenerating the charts, and modifying and re-writing the steps of sorting.

\subsection*{Md. Abu Sufyan (2003085)}
Prepared the slides for Selection sort and Insertion sort using LaTeX with Tameem Rahman (2003089). Utilized the article and document prepared by other members of our team.

\subsection*{Tameem Rahman (2003089)}
Assisted Sufyan (2003085) in creating the slide presentation using LaTeX. Wrote the insertion sort part and added pictures to present the slides nicely.

\end{document}
